---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rcmip6

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/eliocamp/rcmip6/branch/main/graph/badge.svg)](https://app.codecov.io/gh/eliocamp/rcmip6?branch=main)
[![R-CMD-check](https://github.com/eliocamp/rcmip6/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/eliocamp/rcmip6/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of rcmip6 is to search and download data from the CMIP6 project. 

## Installation

You can install the development version of rcmip6 like so:

``` r
remotes::install_github("eliocamp/rcmip6")
```

## Example

Search models, variables, etc... using `cmip_search()`

```{r example}
library(rcmip6)

query <- list(
  type               = "Dataset",
  replica            = "false",
  latest             = "true",
  variable_id        = "tas",
  project            = "CMIP6",
  frequency          = "mon",                          
  table_id           = "Amon",
  experiment_id      = "historical",
  source_id          = "CanESM5"
)

results <- cmip_search(query)
cmip_info(results)
```

Sumary of results:

```{r}
results |> 
  cmip_simplify() |>   # To keep only the most informative columns
  subset(, select = -full_info) |> 
  head(10) |> 
  knitr::kable()
```

The, download the data.
Just as a demonstration, download only the first result

```{r}
cmip_root_set("readme_example")   # Set the root folder where to save files 
options(timeout = 360)            # Kind of important for some reason

files <- cmip_download(results[1])
```

The files are saved mirroring the source file structure to ensure that each file is unique. 

```{r}
fs::dir_tree(cmip_root_get())
```

This structure can be parsed with `cmip_available()`

```{r}
cmip_available()
```

We can obtain the urls that *would* be downloaded.  

Note that these are the *file server* URLs, in at lease some cases we can substitute "/fileServer/" with "/dodsC/" for the OpenDAP server URLs, which will work remotely with the NetCDF API. 

```{r urls}
urls <- cmip_urls(results)
str(urls)
basename(urls[1:3])
```
